Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2021-01-19 journal paper/content/sec-model.tex
Space-saving

Our models are stylized in several important  respects. Firms compete only on the quality of service, rather than, say, pricing or the range of products. Agents are myopic: they do not worry about how their actions impact their future utility.\footnote{So, agents do not attempt to learn over time, second-guess or game future agents, or manipulate the principals' learning algorithms. This is arguably typical in practice, in part because one agent's influence tends to be small.}  Various performance signals available to the users, from personal experience to word-of-mouth to consumer reports, are abstracted as persistent ``reputation scores" reflecting the current reputation, and further simplified to average performance over a sliding time window.

>>>>

Our models are stylized in several important  respects. Firms compete only on the quality of service, rather than, say, pricing or the range of products. Agents are myopic: they do not worry about how their actions impact their future utility.\footnote{So, agents do not attempt to learn over time, game future agents, or manipulate the principals' learning algorithms. This is arguably typical in practice, in part because one agent's influence tends to be small.}  Various performance signals available to the users, from personal experience to word-of-mouth to consumer reports, are abstracted as persistent ``reputation scores" reflecting the current reputation, and further simplified to average performance over a sliding time window.
